Model details and results

### 2023-09-25 notebook/model-details.qmd
Create a temporary no-stripe class for gt tables
bc of https://github.com/quarto-dev/quarto-cli/issues/6945

```{r mcmc-duration-table}
models |> 
  gt() |> 
  tab_footnote(
    footnote = "Duration of the longest-running MCMC chain",
    locations = cells_column_labels(columns = total)
  ) |> 
  cols_label(
    model_name = "Model",
    total = "Total time"
  ) |> 
  cols_align(
    align = "left",
    columns = everything()
  ) |>
  fmt_markdown(columns = model_name) |> 
  grand_summary_rows(
    columns = c(total),
    fns = list(`Overall total` = ~as.duration(sum(.)))
  ) |> 
  opt_footnote_marks(marks = "standard") |> 
  opt_horizontal_padding(3) |> 
  opts_theme()
```

@@

```{r results-table}
modelsummary(
  m_full_ordbeta,
  statistic = "[{conf.low}, {conf.high}]",
  ci_method = "hdi",
  metrics = c("R2"),
  output = "gt"
) |> 
  opts_theme()
```

>>>>

```{r mcmc-duration-table}
#| classes: no-stripe
models |> 
  gt() |> 
  tab_footnote(
    footnote = "Duration of the longest-running MCMC chain",
    locations = cells_column_labels(columns = total)
  ) |> 
  cols_label(
    model_name = "Model",
    total = "Total time"
  ) |> 
  cols_align(
    align = "left",
    columns = everything()
  ) |>
  fmt_markdown(columns = model_name) |> 
  grand_summary_rows(
    columns = c(total),
    fns = list(`Overall total` = ~as.duration(sum(.)))
  ) |> 
  opt_footnote_marks(marks = "standard") |> 
  opt_horizontal_padding(3) |> 
  opts_theme()
```

@@

```{r results-table}
#| classes: no-stripe
modelsummary(
  m_full_ordbeta,
  statistic = "[{conf.low}, {conf.high}]",
  ci_method = "hdi",
  metrics = c("R2"),
  output = "gt"
) |> 
  opts_theme()
```
